The not so widening achievement gap: an interntational comparison of the evolution of the SES achievement gap from 2000-2015

### 2017-08-02 paper/paper.Rnw
Updated to run lm separate for each country when adjusting cognitive variable

# It returns a dataframe for each survey with all countries and respective coefficients and
# standard errors.
test_diff <- function(df, reliability, test, probs) {

@@

      # Calculate median math score of all PV's
      .x$dv <- apply(.x[test_vars], 1, median, na.rm = T)
      .x$dv <- rowMedians(as.matrix(.x[test_vars]), na.rm = T)

      # Should I estimate the model separately by country?
      mod1 <- lm(dv ~ AGE,
                 weights = .x[[weights_var]],
                 data = .x,
                 na.action = "na.exclude")

      # Take residuals of model and divide by rmse. Multiply that by
      # 1 / sqrt(reliability of each survey), which is .y in the loop.
      .x$adj_pvnum <- resid(mod1)/rmse(mod1, .x) * 1 / sqrt(.y)

>>>>

# It returns a dataframe for each survey with all countries and respective coefficients and
# standard errors.

test_diff <- function(df, reliability, test, probs) {

@@

      # Calculate median math score of all PV's
      .x$dv <- rowMedians(as.matrix(.x[test_vars]), na.rm = T)

      # Should I estimate the model separately by country?
      separate_countries <-
        .x %>%
        split(.x$country) %>%
        map(function(each_country) {
        mod1 <- lm(dv ~ AGE,
                   weights = each_country[[weights_var]],
                   data = each_country,
                   na.action = "na.exclude")

      # Take residuals of model and divide by rmse. Multiply that by
      # 1 / sqrt(reliability of each survey), which is .y in the loop.
      each_country$adj_pvnum <- resid(mod1)/rmse(mod1, each_country) * 1 / sqrt(.y)
      each_country
      })

      .x <-
        separate_countries %>%
        reduce(bind_rows)
